---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statZHmatomo

<!-- badges: start -->
<!-- badges: end -->

The goal of statZHmatomo is to provide functions for easy access to the ZHWeb Matomo Reporting API. Web Analystics data is available for the [Daten- und Publikationskatalog](https://www.zh.ch/de/politik-staat/statistik-daten/datenkatalog.html#/home) which is maintained by Statistisches Amt Kanton Zürich. 

The package currently contains only one function `read_matomo_data`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("statistikZH/statZHmatomo")
```

## Prerequisites

The Matomo API Token needs to be added to the .Renviron file before the function `read_matomo_data` can be used. The token is then called via `Sys.getenv("token")`. To add your token, follow these steps:


1. If not already installed, call `install.packages("usethis")`.
2. Call `usethis::edit_r_environ`
3. Add your token on new line as "token = YOUR_TOKEN"
4. Save the .Renviron file
5. Restart R via "Session -> Restart R" or "Ctrl / Cmd + Shift + Enter"

## Example

This is a basic example using the API module 'Action' and the API action 'getPageUrls'.

```{r example, warning=FALSE}

library(statZHmatomo)
library(magrittr)

## basic example code

dat <- read_matomo_data(apiModule = "Actions", apiAction = "getPageUrls") 

dat %>% 
  tibble::as_tibble() %>% 
  janitor::clean_names() %>% 
  dplyr::select(1:8) %>% 
  knitr::kable()

```

